---
title: "p8105_hw6_to2345"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(mgcv)
set.seed(1)

boot_sample = function(df){
  sample_frac(df, replace = TRUE)
}

```

Load the data:
```{r}
bwt = 
  read_csv(file = './birthweight.csv') %>% 
  mutate(
    babysex = as_factor(babysex),
    frace = as_factor(frace),
    malform = as_factor(malform),
    mrace = as_factor(mrace)
  )

table(is.na(bwt))

```
There is no missing values in this dataset.


Proposed regression model 1:
y = baby's birth weight
x = gaweeks
<Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.>

```{r}
model1 = lm(bwt ~ gaweeks, data = bwt)
summary(model1)

# plot of model residuals against fitted values
bwt %>% 
  modelr::add_residuals(model1) %>% 
  modelr::add_predictions(model1) %>% 
  ggplot(
    aes(x = pred,
        y = resid)
  ) +
  geom_point() +
  ggtitle("Residuals against fitted values <Model 1>") +
  theme_minimal()



```


Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only) -- Model 2
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these -- Model 3

```{r}
model2 =
  lm(bwt ~ blength + gaweeks, data = bwt)

model3 =
  lm(bwt ~ bhead * blength * babysex, data = bwt)

# Cross validation between these 3 models

cv_df = crossv_mc(bwt, 100)
cv_df =
  cv_df %>% 
  mutate(
    model1 = map(train, ~lm(bwt ~ gaweeks, data = bwt)),
    model2 = map(train, ~lm(bwt ~ blength + gaweeks, data = bwt)),
    model3 = map(train, ~lm(bwt ~ bhead * blength * babysex, data = bwt))
  ) %>% 
  mutate(
    rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
    rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y))
  )

# Plotting the distribution of RMSE values for each candidate model
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  theme_minimal()+
  ggtitle("Distribution of RMSE values across three different models")

```

- It is clear that Model 3 (using head circumference, length, sex, and all interactions as variables) has the least RMSE values, compared to the other two models.


